
%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/



\documentclass[10pt, conference, letterpaper]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[bookmarks=false]{hyperref}
\usepackage{cite}
\usepackage[dvips]{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{caption}
\usepackage{array}
\usepackage{verbatim}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{url}
\usepackage{color}
\usepackage{listings}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{booktabs}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
%\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}



% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}





\hyphenation{op-tical net-works semi-conduc-tor}



\begin{document}

% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{MicroPrivacy: \\Detection of Visual Eavesdroppers on Smartphones}
%Detection of Visual Eavesdroppers to Preserve Privacy on Smartphones }


% author names and affiliations
% use a multiple column layout for up to three different
% affiliations

%\author{
%\IEEEauthorblockN{Hui Wen$^{1,2}$, Qiang Li$^{1,2}$, Qi Han$^{3}$, Shiming Ge$^{1}$,Limin Sun$^{1}$\thanks{\small{Limin Sun is the corresponding author.}}
%}
%\IEEEauthorblockA{
%$^1$Institute of Information Engineering,CAS,Beijing, Beijing, China 100093
%\\$^2$University of Chinese Academy of Sciences, Beijing, China 100093
%\\$^3$Department of EECS, Colorado School of Mines, Golden, CO USA 80401
%\\ Email:\{{wenhui,liqiang43,geshiming,sunlimin\}}@iie.ac.cn, qhan@mines.edu
%}
%
%}

\author{}


% make the title area
\maketitle


%\begin{abstract}
%%\boldmath
%Visual eavesdropping refers to a scenario that a person tries to read the content displayed on another person's mobile phone screen over the shoulder of that person while trying to be unobtrusive.
%We present an interesting approach that detects visual eavesdroppers in order to preserve privacy on mobile phones. The proposed detection method relies on computer vision and image processing algorithms running on the video streams from the front camera  built in most commodity mobile phones.
%Considering the limitations of a mobile phone's computation power and camera's field of view, we propose effective pre-processing techniques to reduce computation needs.  We further combine face detection and motion detection methods to improve the accuracy for detecting  visual eavesdroppers in different scenes. For situations in which a visual eavesdropper moves into an area not detectable by the front camera, we design a maximum likelihood estimation method to predict the probability of potential visual eavesdropping.
%We present the design and implementation of visual eavesdroppers detection method.  We evaluate the proposed method using a series of experiments.  Our empirical studies show that the proposed technique achieves high detection accuracy.
%\end{abstract}

\input{abstract}

\IEEEpeerreviewmaketitle


\input{intro.tex}

\input{relate}

\input{design_Consideration.tex}

\input{System_Detailed_Design.tex}

\input{Experiments.tex}





\section{Conclusion}
In this paper, we define the problem of  visual  eavesdropping  and propose a method to detect it for preserving user privacy on smartphone. We conduct a variety of  experiments to evaluate the effectiveness of the proposed method  public datasets and real-world experiments.  This work can help alert people of potential eavesdropping.  In the future, we will complement this work by protecting user privacy via image distortion and masking when potential privacy leakage is detected.

Since MicroPrivacy is a CV based approach, its performance is limited by the performance of CV techniques.  When there are multiple people walking around the phone user or the background has significant light variation, the accuracy of face detection drops. Nevertheless, MicroPrivacy can work well in many scenarios, especially in a spacious place or  room with few people.  Our work shows that CV based methods have a great potential especially in the future when CV techniques become more robust and efficient. Further, there is a special scenario that a person may be looking in the direction of the smart-phone, he may not be looking at the smartphone. In this case,  MicroPrivacy takes a conservative approach by alerting the phone user anyway, without trying to differentiate between the two cases.  High energy consumption is another problem in CV based approaches on smartphones. To address this problem, a few pieces of work have already started investigating how to reduce the computation\cite{mobilevision}.  We believe these efforts along with the advances in smartphone hardware will make it acceptable to have CV based apps on smartphones. 

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,mobile}




% that's all folks
\end{document}


